\thetitle

### 2020-07-07 writing/landscape.tex
sec 3: fix cites, add missing paren

Typed Racket extends the untyped Racket language with \emph{natural}\/ gradual
 types~\cite{}.
Natural types guarantee a strict separation between typed and untyped code;
 informally, an untyped value can interact with a typed context only if the
 value behaves in a well-typed way.
Typed Racket implements this separation by compiling types to higher-order
 contracts that guard all boundaries to untyped code.
Any higher-order typed value that exits a boundary receives a protective
 wrapper, and any untyped value that enters must pass a deep run-time type
 check.
These contract checks help predict the behavior of typed code, but
 may greatly slow down a program.

@@

Second, transient adds a new pass to the compiler that rewrites all typed code.
Rewriting changes all elimination forms to shape-check the result.
For example, if the variable {\tt f} has the static type {\tt (-> String String)}
 then the application {\tt (f x}} must be rewritten to check for a string result
 because {\tt f} could be an untyped function.
Rewriting also inserts hooks to update a global blame heap.
When a value crosses a boundary, the blame heap records a cast assumption.
Elimination forms and other operations record smaller path assumptions.
If a transient check ever fails, the language follows path assumptions and
 reports a set of casts/boundaries to the programmer.

>>>>

Typed Racket extends the untyped Racket language with \emph{natural}\/ gradual
 types~\cite{tf-popl-2008,tfffgksst-snapl-2017}.
Natural types guarantee a strict separation between typed and untyped code;
 informally, an untyped value can interact with a typed context only if the
 value behaves in a well-typed way.
Typed Racket implements this separation by compiling types to higher-order
 contracts that guard all boundaries to untyped code.
Any higher-order typed value that exits a boundary receives a protective
 wrapper, and any untyped value that enters must pass a deep run-time type
 check.
These contract checks help predict the behavior of typed code, but
 may greatly slow down a program.

@@

Second, transient adds a new pass to the compiler that rewrites all typed code.
Rewriting changes all elimination forms to shape-check the result.
For example, if the variable {\tt f} has the static type {\tt (-> String String)}
 then the application {\tt (f x)} must be rewritten to check for a string result
 because {\tt f} could be an untyped function.
Rewriting also inserts hooks to update a global blame heap.
When a value crosses a boundary, the blame heap records a cast assumption.
Elimination forms and other operations record smaller path assumptions.
If a transient check ever fails, the language follows path assumptions and
 reports a set of casts/boundaries to the programmer.
